ggalluvial: Layered Grammar for Alluvial Plots

### 2020-05-21 README.rmd
docs(readme): reorganize badges + add JOSS paper

[![Travis build status](https://travis-ci.org/corybrunson/ggalluvial.svg?branch=master)](https://travis-ci.org/corybrunson/ggalluvial)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/ggalluvial)](https://cran.r-project.org/package=ggalluvial)
[![JOSS](https://joss.theoj.org/papers/2a38fbb08d94994145d01c370f243723/status.svg)](https://joss.theoj.org/papers/2a38fbb08d94994145d01c370f243723)

>>>>

[![Travis](https://travis-ci.org/corybrunson/ggalluvial.svg?branch=master)](https://travis-ci.org/corybrunson/ggalluvial)
[![CRAN](http://www.r-pkg.org/badges/version/ggalluvial)](https://cran.r-project.org/package=ggalluvial)

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3836748.svg)](https://doi.org/10.5281/zenodo.3836748)
[![JOSS](https://joss.theoj.org/papers/10.21105/joss.02017/status.svg)](https://doi.org/10.21105/joss.02017)
